### 2018-03-08 chapter2/ms.tex
Fix Refs. Chapter 5 Bulk Formatting

\clearpage
\begin{deluxetable}{cccccc}
\tabletypesize{\footnotesize}
\tablecolumns{6}
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}
\tablecaption{Expected Rates For Fast Transients}
\tablehead{
\colhead{Object}&  \colhead{$\mathcal{R}_{\rm vol}$}& \colhead{$z_{\rm max}$}  &  \colhead{$\mathcal{R}_{\rm area}$} &  \colhead{$N$}     &     \colhead{Reference}      \\
\colhead{} & \colhead{(Mpc$^{-3}$ yr$^{-1}$)} & \colhead{} & \colhead{(deg$^{-2}$ yr$^{-1}$)} &  \colhead{} & \colhead{} }
\startdata
 Type .Ia    &                  10$^{-6}$                   &  0.5        &  $0.7$            &         1.4  & \citet{Bildsten+07} \\
 WD-NS mergers  &                  10$^{-5}$                   &   0.06        & $2\times10^{-2}$              &         $3\times10^{-2}$  &     \citet{Thompson2009}     \\
 WD-BH mergers  &      10$^{-5}$                   &    0.06        &   $2\times10^{-2}$              &      $3\times10^{-2}$  &    \citet{Fryer+99}          \\
AIC       &                  10$^{-6}$                   & 0.06        & $2\times10^{-3}$            &        $3\times10^{-3}$ &  \citet{Darbha+10}   \\
ELDD      &                  3$\times 10^{-7}$                   & 0.14        &    $6\times10^{-3}$           &      $1\times10^{-2}$ &  $\cdots$  \\
Pan-STARRS fast &                  5$\times 10^{-6}$                   &     0.5        &   $3.5$            &     7 &   \citet{Drout+14}
\enddata
\tablecomments{Expected rates for the various contaminants considered in \cref{sec:ch2_contaminants}. $\mathcal{R}_{\rm area}$ is computed assuming an isotropic distribution of sources in a volume defined by the comoving volume at $z_{\rm max}$.  The column $N$ refers to the number of events expected during a search covering 100 deg$^2$ for 7 days. See \cref{sec:ch2_rates} or details.}
\label{tab:ch2_rates}
\end{deluxetable}

>>>>

\clearpage
\begin{deluxetable}{cccccc}
\tabletypesize{\footnotesize}
\tablecolumns{6}
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}
\tablecaption{Expected Rates For Fast Transients}
\tablehead{
\colhead{Object}&  \colhead{$\mathcal{R}_{\rm vol}$}& \colhead{$z_{\rm max}$}  &  \colhead{$\mathcal{R}_{\rm area}$} &  \colhead{$N$}     &     \colhead{Reference}      \\
\colhead{} & \colhead{(Mpc$^{-3}$ yr$^{-1}$)} & \colhead{} & \colhead{(deg$^{-2}$ yr$^{-1}$)} &  \colhead{} & \colhead{} }
\startdata
 Type .Ia    &                  10$^{-6}$                   &  0.5        &  $0.7$            &         1.4  & \citet{Bildsten+07} \\
 WD-NS mergers  &                  10$^{-5}$                   &   0.06        & $2\times10^{-2}$              &         $3\times10^{-2}$  &     \citet{Thompson+09}     \\
 WD-BH mergers  &      10$^{-5}$                   &    0.06        &   $2\times10^{-2}$              &      $3\times10^{-2}$  &    \citet{Fryer+99}          \\
AIC       &                  10$^{-6}$                   & 0.06        & $2\times10^{-3}$            &        $3\times10^{-3}$ &  \citet{Darbha+10}   \\
ELDD      &                  3$\times 10^{-7}$                   & 0.14        &    $6\times10^{-3}$           &      $1\times10^{-2}$ &  $\cdots$  \\
Pan-STARRS fast &                  5$\times 10^{-6}$                   &     0.5        &   $3.5$            &     7 &   \citet{Drout+14}
\enddata
\tablecomments{Expected rates for the various contaminants considered in \cref{sec:ch2_contaminants}. $\mathcal{R}_{\rm area}$ is computed assuming an isotropic distribution of sources in a volume defined by the comoving volume at $z_{\rm max}$.  The column $N$ refers to the number of events expected during a search covering 100 deg$^2$ for 7 days. See \cref{sec:ch2_rates} or details.}
\label{tab:ch2_rates}
\end{deluxetable}

### 2018-03-08 chapter4/ms.tex
Fix Refs. Chapter 5 Bulk Formatting

\clearpage
\item We require a $\ge 3\sigma$ decline in flux between the first and
third epochs to search for significant fading\footnote{We note that this
criterion effectively requires the detection in the first epoch to be $\gtrsim 5\sigma$
producing an effectively shallower transient search. Soares-Santos et al.
\citeyearpar{ss+16} quantified this effect by injecting fake sources into
their observations to determine the recovery efficiency and loss of detection
depth from analysis cuts. Here, we forego
such analysis to focus the discussion on the effects of contamination in
optical follow-up of GW events.}. We calculate $\sigma$ as the
quadrature sum of the flux errors from the first and third epochs
($\sigma = \sqrt{\sigma_1^2 + \sigma_3^2}$, where $\sigma_1$ and
$\sigma_3$ are the flux errors from the first and third epochs,
respectively). This criterion leaves a sample of 48 objects.

>>>>

\clearpage
\item We require a $\ge 3\sigma$ decline in flux between the first and
third epochs to search for significant fading\footnote{We note that this
criterion effectively requires the detection in the first epoch to be $\gtrsim 5\sigma$
producing an effectively shallower transient search. Soares-Santos et al.
\citeyearpar{GW150914DECam} quantified this effect by injecting fake sources into
their observations to determine the recovery efficiency and loss of detection
depth from analysis cuts. Here, we forego
such analysis to focus the discussion on the effects of contamination in
optical follow-up of GW events.}. We calculate $\sigma$ as the
quadrature sum of the flux errors from the first and third epochs
($\sigma = \sqrt{\sigma_1^2 + \sigma_3^2}$, where $\sigma_1$ and
$\sigma_3$ are the flux errors from the first and third epochs,
respectively). This criterion leaves a sample of 48 objects.
